% !TEX encoding = UTF-8
%======中文摘要内容格式:{中文摘要}{关键词}
\ZhAbstract{

湖南师范大学“计算与随机数学”教育部重点实验室依托基础数学全国重点培育学科，数学国家211工程重点建设学科，湖南省数学国内一流建设学科和统计学国内一流培育学科，数学、统计学一级学科博士点进行建设。其历史可追溯到上个世纪90年代初的湖南师范大学计算机研究所，后该所与数学系等单位合并成立理学院，2002年成立数学实验室，2007年成立“计算与随机数学及其应用”校级重点实验室，同年该实验室获批为湖南省普通高等学校重点实验室，2009年批准立项建设“高性能计算与随机信息处理”省部共建教育部重点实验室，2010年4月召开实验室建设计划现场论证会，实验室正式启动建设，并于2013年12月通过教育部组织的验收，2018年因实验室发展需要更名为“计算与随机数学”教育部重点实验室。
}{湖南师范大学，计算与随机数学，教育部重点实验室。}

%======中文摘要内容格式:{英文摘要}{关键词}



\EnAbstract{
	Hunan Normal University's "Computation and Stochastic Mathematics" key laboratory of the Ministry of Education relies on the national key cultivation discipline of basic mathematics, the national 211 project key construction discipline of mathematics, the first-class construction discipline of mathematics in Hunan Province and the first-class domestic training discipline of statistics, and the first-class discipline of mathematics and statistics. The construction of a doctoral program of the first-level discipline. Its history can be traced back to the Computer Research Institute of Hunan Normal University in the early 1990s. Later, the Institute merged with the Department of Mathematics and other units to form the School of Science. In 2002, the Mathematics Laboratory was established. "School-level key laboratory. In the same year, the laboratory was approved as a key laboratory of ordinary colleges and universities in Hunan Province. In 2009, it was approved to establish a key laboratory of "high performance computing and random information processing" jointly established by the Ministry of Education and the Ministry of Education. On-site demonstration meeting of the laboratory construction plan was held in January, and the laboratory officially started construction, and passed the acceptance organized by the Ministry of Education in December 2013. In 2018, due to the development of the laboratory, it was renamed the "Computation and Stochastic Mathematics" Key Laboratory of the Ministry of Education.
}{Hunan Normal University, Computational and Stochastic Mathematics, Key Laboratory of the Ministry of Education.}
